### 2012-11-29 inst/examples/singular-inversion.Rmd
print determinant value

``` {r}
d <- gp_fit(obs, X, c(sigma_n=1, l=.0001, tau=.3), "direct")
plot.gpfit(d)
```

``` {r}
d <- gp_fit(obs, X, c(sigma_n=1, l=10, tau=.3), "direct")
plot.gpfit(d)
```

>>>>

Fit with reasonable choice of length scale `l`

``` {r}
d <- gp_fit(obs, X, c(sigma_n=.5, l=.02, tau=.3), "direct")
det(d$K + .5^2 * diag(1, length(X)))
plot.gpfit(d)
```

Fit with long length scales.

``` {r}
d <- gp_fit(obs, X, c(sigma_n=.5, l=10, tau=.3), "direct")
det(d$K + .5^2 * diag(1, length(X)))
plot.gpfit(d)
```
